Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2017-10-27 paper/main.tex

\subsection{Synthetic Experiment}
In order to demonstrate how PLR may be used to speed up tasks that the LSTM is
well-suited for, we tackle a pathological inference problem first introduced
in Hochreiter and Schmidhuber's initial LSTM paper \cite{hochreiter1997long}.
The input consists of sequences of length $n$ with each sequence element a randomly
chosen one-hot vector in $p$ dimensional space.
The first vector in each sequence is always the same, up to the sign of the component (i.e. it is $\pm
\boldsymbol{p_0}$). The sequential model must read in an entire sequence and then output
the sign of the first sequence element.
This sequence classification problem requires remembering the first element over the length of the
sequence and is a canonical example of the long-term dependency problem.
Due to the large throughput of the GILR-LSTM, we would expect that it
would do better when the sequence length is large. In the original formulation
of the problem (dealing in the regime with around one hundred timesteps)
, $p$ is set equal to $n$. As this would make the size of the input data
grow impracticaly large as \(\mathcal{O}(n^2)\) for long sequences, we fix \(p =
128\) and vary \(n\).

>>>>

\subsection{Synthetic Experiment}
In order to demonstrate how PLR may be used to speed up tasks that the LSTM is
well-suited for, we tackle a pathological inference problem first introduced
in Hochreiter and Schmidhuber's initial LSTM paper \cite{hochreiter1997long}.
The input consists of sequences of length $n$ with each sequence element a randomly
chosen one-hot vector in $p$ dimensional space.
The first vector in each sequence is always the same, up to the sign of the component (i.e. it is $\pm
\boldsymbol{p_0}$). The sequential model must read in an entire sequence and then output
the sign of the first sequence element.
This sequence classification problem requires remembering the first element over the length of the
sequence and is a canonical example of the long-term dependency problem.
Due to the large throughput of the GILR-LSTM, we would expect that it
would do better when the sequence length is large. In the original formulation
of the problem (dealing in the regime with around one hundred timesteps)

, \(p\) is set equal to \(n\). Since this would make the size of the
input data grow impractically large as \(\mathcal{O}(n^2)\) for long
sequences, we fix \(p = 128\) and vary \(n\).
